Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
improve running example section

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed 
a high-performance controller, which is characterised by the following z-domain transfer function:
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $G(z)$.  
However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point arithmetic 
and word-length), then this controller becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16} implementation format 
({\it i.e.}, $4$ bits for the integer part and $16$ bits for the fractional part)
can be represented by the following expression: 
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
}
\end{equation} 
which makes the system unstable in closed-loop using fixed-point arithmetic and 
the typical series loop configuration, where $C_{q}\left(z\right)$ and $G\left(z\right)$ 
are in the forward path.

>>>>

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed 
a high-performance controller, which is characterised by the following z-domain transfer function:
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
The authors claim that this controller $C(z)$ stabilizes the closed-loop system for the discrete plant model $G(z)$.  
However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point arithmetic 
and word-length), then this closed-loop system becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16} implementation format 
({\it i.e.}, $4$ bits for the integer part and $16$ bits for the fractional part)
can be represented by the following expression: 
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
}
\end{equation} 
which makes the system unstable in closed-loop using fixed-point arithmetic and 
the typical series loop configuration, where $C_{q}\left(z\right)$ and $G\left(z\right)$ 
are in the forward path.
